\input{preamble}


\begin{document}

\linenumbers

\title{The Readout Sequence for the \minerva CROC-E}

\author[1]{G.~N.~Perdue}
\affil[1]{\Rochester}

\maketitle

\abstract{We describe the readout sequence commands for the \minerva CROC-E.}

\section{Introduction}
\label{sec:introduction}

This document describes the commands required to readout the \minerva CROC-E.
% \cite{refcroce} - No DocDB available yet.
We assume there is interesting data sitting on the FEB in this document.

\section{CROC+ Mode: Sequencer Readout Disabled}
\label{sec:seqreaddisab}

Tentative sequence (assuming one FEB); all addresses assume CROCE Base + Channel Offset Address ($i \times \hex{4000}$):
\begin{enumerate}
\item Configuration (\hex{28002}): \hex{0001} to disable the Sequencer Readout mode and set the number of FEBs to one.
\item Command (\hex{2804}): \hex{B000} to clear the status register and reset both the send and receive memory pointers.
\item Read the Frame (\hex{28020}) and Tx/Rx (\hex{28040}) Status registers? Or only one?
\item Write the frame we would like to send/read to the Send Memory Register (\hex{22000}). 
\item Write send message (\hex{40000}) to the Command Register (\hex{28004}) to send the message.
\item Poll the status register looking for Sequencer Done and Frame Received bits to go to one (mask for those two bits: \hex{0410}). Once both bits are one, we may begin readout. What value of the register constitutes perfect health?
\item Read the Receive Memory Pointer (\hex{28080}) to get the amount of data.
\item Read the Receive Memory Register (\hex{00000}), using the result from the pointer read, to get that many bytes. 
\item At the end of readout, optionally read the Event Counter register (\hex{28008}).
\end{enumerate}


\section{CROC+ Mode: Sequencer Readout Enabled}
\label{sec:seqreadenab}

Tentative sequence (assuming one FEB); all addresses assume CROCE Base + Channel Offset Address ($i \times \hex{4000}$):
\begin{enumerate}
\item Configuration (\hex{28002}): \hex{8001} to enable the Sequencer Readout mode and set the number of FEBs to one.
\item Command (\hex{2804}): \hex{B000} to clear the status register and reset both the send and receive memory pointers.
\item Read the Frame (\hex{28020}) and Tx/Rx (\hex{28040}) Status registers? Or only one?
\item Send an RDFE signal.
\item Poll the status register looking for Sequencer Done and Frame Received bits to go to one (mask for those two bits: \hex{0410}). Once both bits are one, we may begin readout.
\item Read the Receive Memory Pointer (\hex{28080}) to get the amount of data.
\item Read the Receive Memory Register (\hex{00000}), using the result from the pointer read, to get that many bytes. In this case, we have a glob with all the frame data from the FEB.
\item At the end of readout, optionally read the Event Counter register (\hex{28008}).
\end{enumerate}

\section{CROC+ Mode: Reading and Clearing the CROC Status Register}
\label{sec:readandclearcrocstatus}



\section{CROC+ Mode: Reading Data from the FEBs}
\label{sec:readfromfebs}


\section{CROC+ Mode: Writing Data to the FEBs}
\label{sec:writetofebs}


\bibliographystyle{plain}
\bibliography{DAQElectronics}

\end{document}
